Finite Complete Suites for CSP Refinement Testing

### 2018-11-26 scp-journal/article/complexity.tex
Considered message of 25.11

An arbitrary CSP process $P$ might have $\minhits(P/s) = \varnothing$ for
some traces $s$, so that a test case $U_F(j)$ for a $j$ greater than the size
of $s$ can enter branch~(\ref{eq:ufb}). In this case, further executions are
needed to consider traces that have $s$ as a prefix.  To provide a bound on
the number of test executions needed, we first define a process $\pmax$~(see
(\ref{eq:pmax})), which, when used as a reference process, requires the
maximal number of test executions among all reference processes $P$
fulfilling $\minhits(P/s) != \varnothing$ for all traces $s$. For $\pmax$, we
can establish the actual number of test executions required~(see
(\ref{eq:pmaxcomplexity})).

>>>>

An arbitrary CSP process $P$ might have $\minhits(P/s) = \varnothing$ for
some traces $s$, so that a test case $U_F(j)$ for a $j$ greater than the size
of $s$ can enter branch~(\ref{eq:ufb}). In this case, further executions are
needed to consider traces that have $s$ as a prefix.  To provide a bound on
the number of test executions needed, we first define a process $\pmax$~(see
(\ref{eq:pmax})), which, when used as a reference process, requires the
maximal number of test executions among all reference processes $P$
fulfilling $\minhits(P/s) \neq \varnothing$ for all traces $s$. For $\pmax$,
we can establish the actual number of test executions required~(see
(\ref{eq:pmaxcomplexity})).
